\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-11-09 response2.tex
Small updates to responses

\begin{response}
  As part of addressing the referee's primary comment, we have introduced an extra claim which shows that, for any $v\in V(G)$, there is a path in $H$ from $v$ to $a(v)$ of length at most $k-1$ in which $v$ participates in every vertex on this path, including $a(v)$.  We have rephrased this confusing sentence and replaced it with a reference to this claim.
\end{response}

@@

\begin{response}
  We have added an explanation, prior to this, of how to eliminate the possibility that an edge of $F$ bounds a face with with only two vertices and two parallel edges.  Simply apply induction on the cycle $F'$ that uses the second of the parallel edges rather than the first.  This is valid since $F'$ has fewer faces in its interior.
\end{response}

@@

\begin{response}
  We have replaced "appropriate" with the "root of tree in $T$ that contains $v$".
\end{response}

@@

18. page 21, Lemma 27. Should be “labelled a nation or a lake” in the
first paragraph. In the third paragraph, the graph $\hat{G}_1$ should be “edge-maximal” or similar.

\textcolor{orange}{DW: First point fixed. I have suggested words to add. }

\tba
\end{document}

>>>>

\begin{response}
  As part of addressing the referee's primary comment, we have introduced an extra claim which shows that, for any $x\in V(H)$ and any $v\in Y_x$, there is a path in $H$ from the $x$ to $a(v)$ of length at most $k-1$ in which $v$ participates in every vertex on this path, including $a(v)$.  We have rephrased the confusing sentence and replaced it with a reference to this claim.
\end{response}

@@

\begin{response}
  We have added an explanation, prior to this, of how to eliminate the possibility that an edge of $F$ bounds an inner face with with only two vertices and two parallel edges.  Simply apply induction on the cycle $F'$ that uses the second of the parallel edges rather than the first.  This is valid since $F'$ has fewer faces in its interior.
\end{response}

@@

\begin{response}
  We have replaced ``appropriate vertex'' with ``the root of tree in $T$ that contains $v$.''
\end{response}

@@

18. page 21, Lemma 27. Should be “labelled a nation or a lake” in the
first paragraph.

In the third paragraph, the graph $\hat{G}_1$ should be “edge-maximal” or similar.

\begin{response}
  We have added the edge-maximal qualifier and (earlier) defined what it means for a framed graph to be edge-maximal (with respect to its frame).
\end{response}

\end{document}
